A Survey on Ordered Binary Decision Diagrams

### 2015-09-15 paper.tex
Remove BMD paragraph
Add BED intro

The bit vector are \textit{sparse} in the sense that the set contains much less
than $2^n$ vectors and the bit vectors themselves have many zero elements. ZBDDs
are similar to OBDDs but they use a different reduction rule, exploiting the
sparse bit vectors. In ZBDDs, nodes can be eliminated whenever setting the
corresponding variable to 1 yields 0 as result, which is often the case for sparse
bit vectors. This representation proved successful to solve some combinatorial
problems~\cite{BRYANT95}. \tbr

\paragraph*{Binary Moment Diagrams}
\mbox{} % workaround to get line break after paragraph

\tbd

@@

\tbd

>>>>

The bit vector are \textit{sparse} in the sense that the set contains much less
than $2^n$ vectors and the bit vectors themselves have many zero elements. ZBDDs
are similar to OBDDs but they use a different reduction rule, exploiting the
sparse bit vectors. In ZBDDs, nodes can be eliminated whenever setting the
corresponding variable to 1 yields 0 as result, which is often the case for sparse
bit vectors. This representation proved successful to solve some combinatorial
problems~\cite{BRYANT95}. \tbr \newpage

@@

In 1997, Andersen and Hulgaard~\cite{ANDERSEN97} proposeded extending OBDDs with
a third type of nodes representing \textit{operators}. The resulting
representation is referred to as \textit{Binary Expression Diagram}
(\textit{BED}). Such an operator node $n$ has one attribute $op(n)$, the binary
Boolean operator, and, like nonterminal nodes, two children $lo(n)$ and $hi(n)$.
Operator nodes represent their corresponding Boolean connectives in the BED graph.
 \tbr
